\section*{Introduction}
In this document I am proposing a standard data model for VSIPL. To be fair this is my notion of what a data model is. If there is some formal document describing what a data model is I don't know about it. The goal is for the VSIPL data model to be language independent.
\\[6pt]
To start I think the data model presented here is the same as in \cvl{} but I will call it the \jv{} data model so that if nobody else wants to participate in the discussion I will have a data model I can use for my own research interests.  I don't want to limit myself to just what is defined in the VSIPL 1p3 specification but I will try to generalize the ideas so they may be extended.
\\[6pt]
I don't expect this model to necessarily be complete as described here but I do expect it to be a starting point.  There may be some fuzzy sections. There may be some stuff that other folks disagree with. There may be some parts of the model which only apply for a particular language or platform.  But until somebody does a document and some discussion occurs the model will not go anywhere except for \jv.  I do eat my own cooking so to speak.
\\[6pt]
There are four parts to the model. The first is the \Blk{}, the second is the \Vw{}, and a third is the interface between machine dependent data storage and the \Blk{} data storage. When I started this document there were only three parts but I think we need to add in a scalar portion to the data model. Blocks are a storage mechanism for enumerated scalars and without an abstract description for scalars I run into troubles completing the data model. For now I am leaving scalars kind of loosely defined in general and staying with the \cvl{} scalar definitions.  I have started another document for for scalars if we decide to try and tie this down for the general case.
\paragraph{Comment} To go along with developing this model I have tried to understand what has happened with the C++ data model but scanning through my current code base of openvsip is a tough road. I have downloaded the OMG version 1.3 of the VSIP++ spec and will see what I can figure out from it. I need a description of the current C++ data model, and I am  not sure I will be able to suck it out of this spec. The problem is it is easy to ignore any sort of data model and just go willy nilly defining classes and operations which know how to work with underlying data and produce results for a particular programing language and a particular set of requirements but which do not follow any sort of defined data model which is generalizable to multiple languages. So I want to make sure C++ VSIPL did not do that but in-fact do have a well defined approach to data; and it is able to be generalized.
\input{subPurposeApproachGoal}
\input{subNotation}
