\subsection{Purpose, Approach, Goal}
\paragraph{My purpose} for writing this document is to further the discussion of the VSIPL data model to see if we can come up with a common agreement for a generalized VSIPL data model which has enough flexibility for use with any language which one might want to write a VSIPL library for.  
\paragraph{My approach} will be to discuss what I consider the \cvl{} data model to be and add information and insight from what I have learned writing \pyjv{}.  I will attempt some basic UML class diagrams.  I do not know UML so people who know UML need to complain and correct if they think it is needed. Perhaps we can bootstrap some UML documentation for VSIPL in this manner if enough people participate.
\\[6pt]
I also have an example for a Strassen matrix product routine from Golub and Van Loan Matrix Computations algorithm 1.3.1.  I previously implemented that in C++ VSIPL.  I do not know if that example is current with the current VSIPL++ library and I have not been able to install a working library from the current distribution on my systems.  In any case at one time it worked and should still be a valid example for my purposes.  I also have a run-able example for \cvl{} and I used the \cvl{} example as a template for a \pyjv{} example.  So for the current 3 languages of interest I have a common example function that I will use to discuss the data model.
\\[6pt]
There will be some discussion paragraphs where I talk about things I know little about, like the data model for C++ VSIPL, and ask questions or make comments designed to (hopefully) foster some discussion and illumination from the C++ \ttbf{Implementors} and \ttbf{Users}.
\paragraph{Comment}
I have never had much luck with UML either reading it or producing it. I think it may be much overblown as a methodology for specifying systems.  But in case I am wrong, and because so many other seem to think it important, I will attempt some diagrams.  
\paragraph{My goal} is to move the discussion and try to get a few people involved who may be interested in the topic.  If we want to move the spec we need some consensus. If I don't get much interest I will move off and just do my own thing.
